---
title: "Question4"
output: html_document
---

This is EDA project 2 question 4, it will show how have emissions from coal combustion-related sources changed from 1999–2008 across the United States 

first read the data
```{r}
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
library(ggplot2)
```
check data, see what it looks like
```{r}
head(NEI)
str(SCC)
```
In this question, we need first to determine what is coal combustion-related sources.
```{r}
summary(SCC)
```
According to the literature (http://www.epa.gov/ttn/chief/net/2008neiv3/2008_neiv3_tsd_draft.pdf), there are four sectors (EI.Sector) dealing with Coal combustion:
Fuel Comb - Comm/Institutional - Coal
Fuel Comb - Electric Generation - Coal
Fuel Comb - Industrial Boilers, ICEs - Coal
Fuel Comb - Residential - Other
In SCC$SCC.Level.Three we can also find coal.

```{r}
#grepl key word "Coal" from SCC EI.Sector&SCC.Level.Two&SCC.Level.Three
coal1 <- SCC[grepl("Coal|Residential - Other",SCC$EI.Sector),]
nrow(coal1)#nrow of coal1
grep("Coal",SCC$SCC.Level.Two)
#no result of leveltwo
coal2 <- SCC[grepl("Coal",SCC$SCC.Level.Three),]
nrow(coal2) #nrow of coal2
#collect all scc number
coal <- rbind(coal1,coal2)
scc <- coal$SCC
```
there must be some replicate, we choose only unique scc number
```{r}
good <- unique(scc)
length(good)
#197
NEI4 <- NEI[NEI$SCC %in% good, ]
head(NEI4)
```
aggregate data by year, calculate sum coal burn emission
```{r}
nei4 <-  aggregate(Emissions~year,data=NEI4,FUN=sum)
nei4
```
use base plot
```{r}
plot(nei4, type = "n",  xlab = "year", ylab = "total emission",
     main = "Total PM2.5 Coal Combustion Emissions in the US")
lines(nei4)
```
use ggplot
```{r}
ggplot(nei4, aes(x = year, y = Emissions)) +
        geom_point(alpha=.3) +
        geom_smooth(alpha=.2, size=1) +
        ggtitle("Total PM2.5 Coal Combustion Emissions in the US")
```
save picture

